Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2021-02-09 bbbq_article.tex
Rewrite TMH

Transmembrane helices are structurally conserved structures that span
a cell membrane with an alpha helix.
TMHs are hydrophobic, as this is required to span the 
hydrophobic cellular lipid membrane. Additionally,
they often have a length of 23 amino acids to be able to span
the membrane.
Polypeptide fragments derived from TMHs are among the most hydrophobic,
together with the internals of soluble proteins, where the
hydrophobicity parts guide the protein to achieve its 3D configuration.
TMHs are general structures: 25 percent of the human proteome is
anchored by at least one TMH. Also the pathogen SARS-CoV-2 has 21 TMHs, 
making up for 5.5 percent of its entire genome.
There are multiple computational tools developed to predict which
parts of membrane proteins are TMH (\cite{krogh2001predicting,bianchi2017,kall2004combined,arai2004conpred,jones2007improving,klammer2009metatm,wang2019efficient}).

@@

\begin{itemize}
  \item $\mathcal{H}_{1,VB}$: MHC-I has the same percentage of epitopes overlapping
    with viral/bacterial TMHs as with human TMHs
  \item $\mathcal{H}_{2,HVB}$: MHC-II has the same percentage of epitopes overlapping
    with human/viral/bacterial TMHs as expected by chance
  \item $\mathcal{H}_{3}$: TMH and non-TMH regions are equally conserved
    in a proteome
\end{itemize}

>>>>

Transmembrane helices (TMHs) 
are structurally conserved and hydrophobic 
regions of a protein that span a (also hydrophobic) 
cell membrane by an alpha helix of usually 23 amino acids.
Together with the internals of soluble proteins,
peptides derived from TMHs are the most hydrophobic
of a proteome. In both cases, the hydrophobic regions
help shape the protein in its correct 3D configuration.
TMHs are common structures in the proteins of
humans and pathogens. For example, 
15-39\% of the proteins in humans
is predicted to be a membrane protein (\cite{ahram2006estimation}).
There are multiple tools to do in silico predictions 
to determine the transmembrane regions of a protein 
(\cite{krogh2001predicting,bianchi2017,kall2004combined,arai2004conpred,jones2007improving,klammer2009metatm,wang2019efficient}).

@@

\begin{itemize}
  \item $\mathcal{H}_{1,VB}$: MHC-I has the same percentage of epitopes overlapping
    with viral/bacterial TMHs as with human TMHs
  \item $\mathcal{H}_{2,HVB}$: MHC-II has the same percentage of epitopes overlapping
    with human/viral/bacterial TMHs as expected by chance
  \item $\mathcal{H}_{3}$: TMHs and soluble protein regions are equally conserved
    in a proteome
\end{itemize}
